\sys: Light-touch Data-Parallel Shell Processing

### 2020-10-05 paper/draft.tex
Change Figure 2 to minted

\begin{figure}[t]
\centering
\includegraphics[width=0.47\textwidth]{\detokenize{./figs/dish_example.pdf}}
\caption{
  \textbf{Calculating maximum temperatures per year.}
  The script downloads daily temperatures recorded across the U.S. for the years 2015--2020 and extracts the maximum for every year. \kk{Make minted.}
}
\vspace{-15pt}
\label{fig:example}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\begin{minted}[fontsize=\footnotesize]{bash}
base="ftp://ftp.ncdc.noaa.gov/pub/data/noaa";
for y in {2015..2020}; do
 curl $base/$y | grep gz | tr -s" " | cut -d" " -f9 |
 sed "s;^;$base/$y/;" | xargs -n 1 curl -s | gunzip |
 cut -c 89-92 | grep -iv 999 | sort -rn | head -n 1 |
 sed "s/^/Maximum temperature for $y is: /"
done
\end{minted}
% \includegraphics[width=0.47\textwidth]{\detokenize{./figs/dish_example.pdf}}
\caption{
  \textbf{Calculating maximum temperatures per year.}
  The script downloads daily temperatures recorded across the U.S. for the years 2015--2020 and extracts the maximum for every year. \kk{Make minted.}
}
\vspace{-15pt}
\label{fig:example}
\end{figure}
